A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-05 main.tex
%慈悲心 利他心

The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even for cancer patient. Being mindful to patient’s mental health and emotional changes during the dental care. Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. Learning to listen proactively.
Being aware of patient’s spiritual needs during/after treatment.
%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}

@@

empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的
靈性功力
治療關係: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

@@

%% why holistic?
Bruce Lipton introduced mind-brain-body system.
Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
 In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.

@@

%%

genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
The genetics of the cell give us all kinds of potentials. % 自性空

@@

% how placebo effect works?
安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}. Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.

@@

*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛

repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body

@@

Wish and bless the whole world
Dali Lama

>>>>

The spiritual care is the key of holistic healthcare in dental practice\cite{Ling-ChengMong2021} or even more for cancer patient. Being mindful to patient’s mental health and emotional changes during the dental care. Taking patient’s socioeconomic statement and supporting system thoroughly for building a holistic consideration. Learning to listen proactively.
Being aware of patient’s spiritual needs during/after treatment.
%Applying the holistic healthcare strategies, such as the shared decision making, to collect more spiritual-related information of patients in the treating process and adjusting the approaches dynamically.\cite{Ling-ChengMong2021}

@@

empowering
(一)雙方有心理的接觸。
(二)當事人正感到焦慮或不一致(incongruence)。 
(三)治療者在治療關係中是一致的、真實的或真誠的。
(四)治療者能夠對當事人表現出無條件的正向關懷。
(五)治療者能夠同理的瞭解當事人的內在，並努力傳達「我懂你的」。
Personhood: Carl Rogers
尋找生命的意義
真誠、能深刻地善解人意
非認知性核心能力
正念止觀(在當下)
人人有自癒能力
真誠 (Genuineness/Validity/Bona Fides)
內在聲音與外在態度一致/明心見性/超越的意識狀態
(Congruence/Consistency)
共情理解(設身處地/同理心/除我執)
(Empathic Understanding of Reference/Track)
無條件關懷(不批判/頓悟)
(unconditional positive regard)
***引導出案主的無條件自我關懷 => 療癒/復原力（resilience）
諮商員的靈性功力
%治療關係: 
Therapeutic relationship: patient said "I would like to talk about myself more when I visit this doctor who I trusted" % 不自覺就講出，不自主就想要聽從他的建議，不再有抗拒
I find that when I am closest to my inner, intuitive self, when I am somehow in touch with the unknown in me, when perhaps I am in a slightly altered state of consciousness, then whatever I do seems to be full of healing. Then simply my presence is releasing and helpful\cite{Rogers1979}.
%當最接近我的內在、直覺的自我，當我與我內在那不知名的角落（the unknown in me）接觸時(靈性)，當我有一些不一樣的意識狀態時（明心見性），我發現，單純只是我的存在（presence）就能鬆綁案主而且具有療效的。
%Rogers, C. R. The Foundations of the Person-Centered Approach. Education 100, 98–107 (1979).
「診後說三句，更勝良帖十方」

@@

%% why holistic? % Environment 環境
Bruce Lipton introduced mind-brain-body system.
Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
 In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.

@@

%% Environment 環境
genetic determinism 所以我們的科學家依舊在研究，基因對癌症的影響（單向）
The genetics of the cell give us all kinds of potentials. % 自性空

@@

% how placebo effect works? % Environment 改造患者的心，就能改造他的身體環境，有利消除癌症
安慰劑效應的科學研究，驚人地發現現代西方醫學的不確定性。
前額葉背側區 (dorsolateral prefrontal cortex)  是形成安慰劑療效的關鍵(PCA「治療關係」的生理學依據)
the anterior cingulate cortex and the dorsolateral prefrontal cortex have been found to be activated by placebo administration.
\cite{Benedetti2005}\cite{Benedetti2011}\cite{Carlino2011}\cite{Bennett2018}
But modern research, especially the results of neuroimaging studies, has shown unequivocally that placebo-induced analgesia is real in the sense that the neural correlates of the sensation of pain are reduced, in the same way that they would be reduced by a decrease in the intensity of a pain-evoking stimulus or by the administration of an analgesic drug\cite{Eippert2009}\cite{Watson2009}. Today, pain researchers are united in the belief that placebo analgesia is real, in the sense that the neural processes that represent pain are reduced\cite{Bennett2018}.

@@

*** make Figure 5 holistic:
meridian and emotion has mutual reaction
meridian effect tissue and organ
(autonomic nerve system, myofascial network, prefrontal cortex)
placebo-effect influence on drug discovery
博士班學生，越研究越發現，科學的不足，心理與靈性的力量，更是背後推動的冥冥力量，身心靈是合一的。#正念 除了可以減壓，還可以治癒疼痛
Environment 改造患者的心，就能改造他的身體環境，有利消除癌症

% cancer cure (care) 的證明
repentantly confess for not taking care of body and spirit, and sincere thanks for the hard work of my physical body

@@

Dali Lama: Wish and bless the whole world %慈悲心 利他心
% 多了解身心靈的關係，減少癌症對健康的損害
